\section{\sc Employment \\and Experience}
\vspace{2.6pt}

\textbf{Victory Group} \hfill April 2025 - Present \\
Machine Learning Team Lead

Team lead for a team of 4 data scientists and machine learning engineers, responsible for the development of a multimodal (text, audio, classic) AI systems for real-time text and audio processing.

\textbf{Responsibilities:}

\begin{itemize}[left=0pt, label={--}]
    \item Leading the team in the research, development and deployment of a multimodal AI systems.
    \item Mentoring and guiding team members in their professional growth.
    \item Collaborating with cross-functional teams to ensure successful project delivery.
\end{itemize}

\textbf{Achievements:}

\begin{itemize}[left=0pt, label={--}]
    \item Hired and mentored a team of 4 DS and MLE.
    \item Built from scratch all the processes and infrastructure for the team, including:
    \begin{itemize}[topsep=0pt]
        \item Model development and deployment processes
        \item CI/CD pipelines for model deployment
        \item Version control and artifact management
        \item Monitoring, logging and alerting
    \end{itemize}
    \item Under my leadership, the team has successfully developed and deployed:
    \begin{itemize}[topsep=0pt]
        \item A multimodal AI system combining ASR, TTS, and LLM components for real-time phone conversations that achieve human-level performance.
        \item A comprehensive AI solution for automated phone conversation quality assessment and analysis.
    \end{itemize}
\end{itemize}

\textbf{MTS AI} \hfill June 2022 - March 2025 \\
Senior Machine Learning Engineer

Development of a Text-to-Speech, Speech-to-Text, and ASR services that outperform leading competitors in the Russian language.

\textbf{Responsibilities:}

\begin{itemize}[left=0pt, label={--}]
    \item Model deployment using Triton Server, Docker, Kubernetes, Python, and Golang.
    \item Model optimization for performance and resource efficiency:
    \begin{itemize}[topsep=0pt]
        \item Model architecture changes
        \item TensorRT, tritonlang, torchcompile and OpenVINO
        \item Model warmup, quantization, sparsity and pruning
    \end{itemize}
    \item Research, develop, train and fine-tune new model architectures.
\end{itemize}

\textbf{Achievements:}

\begin{itemize}[left=0pt, label={--}]
    \item \textbf{0.12} p95 latency and \textbf{90} RPS for diffusion model on a single \textbf{2g.20Gb} A100 instance.
    \item Established and automated a version-controlled model deployment process using CI/CD, WandB / ClearML, and Artifactory.
    \item The development process was established following best practices (e.g., CI/CD, code review, documentation, unit testing, changelog, semantic versioning, etc.).
    \item Created an automated quality and performance testing in a production-like Kubernetes environment.
    \item Implemented comprehensive observability with monitoring, logging, and alerting.
\end{itemize}

\textbf{Technologies:} \\
Python, Golang, PyTorch, tritonlang, CUDA C++, torchcompile, TensorRT, WandB / ClearML, Triton Server, Observability, Docker + Kubernetes, Git + CI/CD

\textbf{SIRIN} \hfill March 2021 - January 2022 \\
Senior Machine Learning Developer

Designed and implemented machine learning service for the automatic opening of car barriers using computer vision. \\
Achieved \textbf{99\%} accuracy in recognizing Russian license plates and \textbf{90\%} accuracy for all other license plates, maintaining a latency of \textbf{0.5} on a \textbf{4}-core CPU.

\textbf{Technologies:} \\
Python, PyTorch, OpenCV, Docker + Kubernetes, OpenVINO + Triton Server, Observability (Grafana, Kibana, Prometheus), Git + CI/CD

\textbf{ITMO University} \hfill January 2020 - December 2020 \\
Machine Learning Developer

Designed and implemented service for building facade segmentation, managing everything from data collection and preprocessing to model training, evaluation, and deployment.

\textbf{Technologies:} \\
Python, TensorFlow + Keras, OpenCV, Docker, Git

\textbf{SPIIRAS} \hfill August 2018 - October 2020 \\
Middle Machine Learning developer

Designed and implemented facial recognition service, managing everything from data collection/generation and preprocessing to model training, evaluation, and deployment.

\textbf{Technologies:} \\
Python, TensorFlow + Keras, RealSense DepthCamera, OpenCV, Docker, Git

\endinput
